An open source scientific article

### 2021-10-18 src/ms.tex
Initialize figure-dataset

Figure~\ref{fig:my_figure} is an example of a figure that can be generated one of two different ways.
This is useful in the case that the figure is the result of, e.g., a very expensive simulation or MCMC run, which you might not want to ever run on GitHub Actions!
Therefore, two rules exist for generating the figure, and which one gets run depends on whether the code is running on GitHub Actions or locally.
If the code is run locally, the figure is generated from scratch by running the expensive simulation.
The result of the expensive simulation is then uploaded to Zenodo.
Conversely, if the code is run on GitHub Actions, the code downloads the simulation results (skipping the expensive step) and then generates the figure.
Check out the \texttt{Snakefile} and the \texttt{showyourwork.yml} config file for the full implementation of these rules.

% A sample figure generated from an external dataset
\begin{figure}[ht!]
    \begin{centering}
        \includegraphics[width=0.75\linewidth]{figures/my_figure.pdf}
        \caption{
            A sample figure generated from the output of a very expensive simulation.
        }
        % This label tells showyourwork that the script `figures/my_figure.py'
        % generates the PDF included above
        \label{fig:my_figure}
    \end{centering}
\end{figure}

>>>>

Figure~\ref{fig:fibonacci} is an example of a figure that depends on an external dataset.
In order to tell \texttt{showyourwork} about this extra dependency (and how to download it), a custom rule must be added to the \texttt{Snakefile}.

% A sample figure generated from an external dataset
\begin{figure}[ht!]
    \begin{centering}
        \includegraphics[width=0.75\linewidth]{figures/fibonacci.pdf}
        \caption{
            A sample figure showing the Fibonacci sequence in binary.
            This figure was generated from a dataset hosted externally on Zenodo. 
            The instructions for downloading this dataset and making it an explicit dependency of this figure are specified in the \texttt{Snakefile}.
        }
        % This label tells showyourwork that the script `figures/fibonacci.py'
        % generates the PDF included above
        \label{fig:fibonacci}
    \end{centering}
\end{figure}
